---
title: "EM ASSIGNMENT GROUP 5"
output: html_notebook
---



```{r}
library(dplyr)
library(tidyverse)
library(haven)
library(ggplot2)
library(pROC)
library(caret)
```
```{r}

ind=new_ind2012
hh=hh2012
OGData=left_join(ind, hh, by = join_by(IDHH == IDHH))

```


```{r}
# CREATING SUBSET OF THE ORIGINAL DATASET FOR OUR USAGE
df2=OGData %>% select(HHID.y,IDHH,PERSONID,IDPERSON,ME13, ME7, MM3W, MM3M,FM3, FM4A,FM4B,FM4C,MM2W, MM2M,CO22, HHEDUC.y, NPERSONS.y, TR2, TR1, NADULTM.y, NADULTF.y, RC1B1, ID18A, RO5, IN11S1.x, ASSETS2005.x, RO4, RO6, URBAN2011.x, ID13.x, RO3, ED2,ID11.x,ME1,ME2,ME3,ME4,ME5,ME6,ME8,ME2,ME9,ME10, ASSETS.x,ED6,WS4,WS14,WS13,WKSALARY,WKAGLAB,WKNONAG,WKNREGA,WKANY5,SN2H1,SN2H2,FU1,SN2E1,SN2E2,SN2F1,SN2F2,SN2G1,SN2G2,SN2I1,SN2I2,ME14,ME14A,FM5A,FM6A,IN11S4.x,IN11S2.x,RC1B3)

```
```{r}
df2
```





```{r}
df2 <- df2[, -which(names(df2) == "IDPERSON")]
df2 <- df2[, -which(names(df2) == "IDHH")]
```

```{r}
# Define a function to impute missing values with mode
impute_mode <- function(x) {
  if(is.numeric(x)) {
    mode_val <- names(sort(table(x[!is.na(x)]), decreasing = TRUE))[1]
    mode_val <- as.numeric(mode_val)
  } else {
    mode_val <- as.character(names(sort(table(x[!is.na(x)]), decreasing = TRUE))[1])
  }
  x[is.na(x)] <- mode_val
  return(x)
}

# Apply the impute_mode function to every column in the dataset
df2_imputed <- as.data.frame(lapply(df2, impute_mode))

```


```{r}
df2<-df2_imputed
```




**** HERE WE CREATE VARIABLE FOR TV, NEWSPAPER AND NUMBER OF ADULTS  ****

*** watch tv ***


```{r}


df2$watch_TV <-ifelse(df2$RO3 == 1, ifelse(df2$MM3M == 3, 1, 0), ifelse(df2$MM3W == 3, 1, 0))


```

 *** newspaper ***

```{r}

 df2$read_newspaper <- ifelse(df2$RO3 == 1, ifelse(df2$MM2M == 3, 1, 0), ifelse(df2$MM2W == 3, 1, 0))
```

```{r}

df2$num_adult<-df2$NADULTF.y+df2$NADULTM.y


```

**** VARIABLE FOR WIDOW ****

```{r}
df2$hh_ass<-df2$ASSETS2005.x


```

*** HOUSEHOLD ASSETS***
```{r}

df2$Widowed <- ifelse(df2$RO6 == 3,1,0)

# df2[c("Widowed","RO6")]

```

**** VARIABLE FOR FEMALE ****

```{r}

df2$female <- ifelse(df2$RO3 == 2,1,0)
# df2[c("RO3","female")]
```




**** VARIABLE FOR WORKING >=240 HR ****


```{r}


df2$work <- as.numeric(df2$WKAGLAB %in% c(3, 4) | df2$WKANY5 %in% c(3, 4) | 
                        df2$WKSALARY %in% c(3, 4) | df2$WKNREGA %in% c(3, 4) | 
                        df2$WKNONAG %in% c(3, 4))


```





**** VARIABLE FOR LAND HOLDING ****


```{r}

df2$landHolding<- (df2$FM4A-df2$FM6A)/df2$FM3

# df2[c("FM4A","FM4B","FM4C","landHolding")]
```



****  VARIABLE FOR HEAD OF HOUSEHOLD  ****



```{r}


df2$head <- ifelse(df2$RO4 == 1,1,0)
# df2[c("RO4","head")]
```



****  VARIABLE FOR Local government ****



```{r}

df2$local_gov <- ifelse(df2$ME14 == 1 | df2$ME14A==1, 1, 0)


```
```{r}

summary(df2$local_gov)
```

**** Hindu ****

```{r}

df2$hindu <- ifelse(df2$ID11.x == 1,1,0)
# df2[c("hindu")]
```
*** MUSLIM ***

```{r}
# df2["ID11.x"
df2$muslim <- ifelse(df2$ID11.x == 2,1,0)
# df2[c("muslim")]

```
*** CASTE OBC***

```{r}
df2$obc <- ifelse(df2$ID13.x == 3,1,0)
# df2[c("obc")]
```
*** CASTE ST***

```{r}

df2$st <- ifelse(df2$ID13.x == 5,1,0)
# df2[c("st")]

```
*** CASTE SC ***

```{r}

df2$sc <- ifelse(df2$ID13.x == 4,1,0)
# df2[c("sc","ID13.x")]

```
*** Highest Educated adult of family

```{r}

df2$perm_job <- ifelse(df2$WS13 == 4,1,0)
# df2[c("perm_job","WS13")]

```
*** Public meetings and Social org ***
```{r}

df2$social_org <- ifelse(df2$ME7 == 1|df2$ME4 == 1|df2$ME5 == 1|df2$ME6 == 1|df2$ME8 == 1|df2$ME2 == 1|df2$ME10 == 1|df2$ME9 == 1|df2$ME1==1|df2$ME3 == 1,1,0)
df2$public_meet <- ifelse(df2$ME13 == 1,1,0)

```




*** Education and literate***

```{r}
df2$literate <- ifelse(df2$ED2 == 1,1,0)
```

*** Education ***

```{r}
df2$edu <- ifelse(df2$ED6 <= 16, df2$ED6, 17)

```

```{r}
df2$urban <- ifelse(df2$URBAN2011.x == 0, 0, 1)


# df2["urban"]
```
*** Electricity***
```{r}
df2$elec <- ifelse(df2$FU1 == 0, 0, 1)

# df2["elec"]
```
*** Collaboration *** 
```{r}
df2$collab <- ifelse(df2$TR2 == 1, 1, 0)
```

*** BPL *** 
```{r}
df2$BPL <- ifelse(df2$RC1B1 == 1| df2$RC1B3 == 1,1,0)
```

*** Social pension *** 
```{r}
# df2["IN11S1.x"]
df2$socialPen <- ifelse(df2$IN11S1.x == 1 |df2$IN11S2.x == 1 | df2$IN11S4.x == 1, 1, 0)

```



*** Peace Rate *** 
```{r}
# df2["TR1"]
df2$peace <- ifelse(df2$TR1 == 3, 1, 0)


# df2["peace"]
```

*** Asset Poor *** 
```{r}
# df2["ASSETS.x"]

df2$assetPoor<-ifelse(df2$ASSETS.x < 15,1,0)

# df2[c("assetPoor","ASSETS.x")]
```

```{r}
summary(df2)
```

```{r}
summary(df3)
```

```{r}
model <- lm(socialPen~RO5+landHolding+BPL+local_gov+public_meet+social_org,data = df2)
print(model)
```
*** 2005 BEGINS ***
```{r}
ind1=ind2005
# ind1.as_factor()
```

```{r}

hh1=hh2005
```
```{r}
hh11=hh1 %>% select(HHID,IDHH,IDPSU,ME11, ME1, ME2, ME3, ME4, ME5, ME6, ME7, ME8, ME9, MM3A, MM3B,MM2A, MM2B,FU1, HHED5ADULT, NPERSONS, TR2, TR1, NADULTS, RC1A, SN3A,FM2,FM4,SN3F,SN3D,ME12,FM6A)
ind11=ind1 %>% select(PERSONID,CASEID,HHID,IDHH,RO5,HHASSETS,RO4,RO6,URBAN,GROUPS8,RO3,ED2,ED5,WS11A,PERSONID,IDPSU,HHID,IN7,WS6YEAR,IN8,IN10)


df3=left_join(ind11, hh11, by = join_by(IDHH == IDHH))
```


```{r}
df3$socialPen<-ifelse(!is.na(df3$IN7) & df3$IN7==df3$PERSONID ,1,0)
```


```{r}
df3 <- df3[, -which(names(df3) == "IN7")]
df3 <- df3[, -which(names(df3) == "IN8")]
df3 <- df3[, -which(names(df3) == "IN10")]
```


```{r}
# Define a function to impute missing values with mode
impute_mode <- function(x) {
  if(is.numeric(x)) {
    mode_val <- names(sort(table(x[!is.na(x)]), decreasing = TRUE))[1]
    mode_val <- as.numeric(mode_val)
  } else {
    mode_val <- as.character(names(sort(table(x[!is.na(x)]), decreasing = TRUE))[1])
  }
  x[is.na(x)] <- mode_val
  return(x)
}

# Apply the impute_mode function to every column in the dataset
df3_imputed <- as.data.frame(lapply(df3, impute_mode))
df3<-df3_imputed
```





*** CLEANING ***


```{r}
df3$hh_ass<-df3$HHASSETS
# df3["hh_ass"]
```


*** watch tv *** 


```{r}
  
df3$watch_TV <-ifelse(df3$RO3 == 1, ifelse(df3$MM3A == 2, 1, 0), ifelse(df3$MM3B == 2, 1, 0))

```

*** newspaper ***

```{r}

df3$read_newspaper <- ifelse(df3$RO3 == 1, ifelse(df3$MM2A == 2, 1, 0), ifelse(df3$MM2B == 2, 1, 0))
# df3[c("RO3","MM2A","MM2B","newspaper")]
```


*** num adult *** 

```{r}
df3$num_adult<-df3$NADULTS
```

**** VARIABLE FOR WIDOW ****

```{r}

df3$Widowed <- ifelse(df3$RO6 == 3,1,0)
# df3[c("RO6","Widowed")]
```
***

**** VARIABLE FOR FEMALE ****

```{r}
# df3["RO3"]
df3$female <- ifelse(df3$RO3 == 2,1,0)
# df3[c("RO6","Widowed")
```
***

**** VARIABLE FOR HEAD OF HH****

```{r}
# df3["RO4"]
df3$head <- ifelse(df3$RO4 == 1,1,0)
# df3[c("RO6","Widowed")]
```



**** VARIABLE FOR LOCAL GOVT CONN**

```{r}
# df3["SN3A"]
df3$local_gov<-ifelse((df3$ME12 == 2) | (df3$ME12 == 1),1,0)
```



**** VARIABLE FOR HINDU****

```{r}
# df3["GROUPS8"]
# df3$head <- ifelse(df3$RO4 == 1,1,0)
df3$hindu <- ifelse(df3$GROUPS8==1|df3$GROUPS8==2|df3$GROUPS8==3|df3$GROUPS8==4|df3$GROUPS8 ==5,1,0)
# df3[c("GROUPS8","hindu")]
```
**** VARIABLE FOR MUSLIM****

```{r}
# df3["GROUPS8.x"]
df3$muslim <- ifelse(df3$GROUPS8 == 6,1,0)
# df3[c("RO6","Widowed")]
```
**** VARIABLE FOR obc****

```{r}
df3$obc <- ifelse(df3$GROUPS8 == 3,1,0)
```
**** VARIABLE FOR st****

```{r}
df3$st <- ifelse(df3$GROUPS8 == 5,1,0)
```

**** VARIABLE FOR sc****

```{r}
df3$sc <- ifelse(df3$GROUPS8 == 4,1,0)
```

**** VARIABLE FOR SOCIAL ORG**

```{r}
df3$social_org <- ifelse(df3$ME6 == 1|df3$ME7 == 1|df3$ME1 == 1|df3$ME2 == 1|df3$ME3 == 1|df3$ME4 == 1|df3$ME5 == 1|df3$ME8 == 1|df3$ME9 == 1,1,0)
```


**** VARIABLE FOR PUBLIC MEET**

```{r}
df3$public_meet<-ifelse(df3$ME11 == 1,1,0)
```

**** VARIABLE FOR LITERATE****

```{r}
df3$literate <- ifelse(df3$ED2 == 1,1,0)
```
**** VARIABLE FOR EDUCATION****

```{r}
df3$edu<-df3$ED5
```
**** VARIABLE FOR URBAN****

```{r}
df3$urban<-ifelse(df3$URBAN == 1,0,1)
```

**** VARIABLE FOR ELECTRICITY****

```{r}
df3$elec<-ifelse(df3$FU1 == 1,0,1)

```
*** ASSET POOR ***
```{r}
df3$assetPoor<-ifelse(df3$HHASSETS < 11,1,0)

```

*** COLLABORATION ***
```{r}

df3$collab<-ifelse(df3$TR2==1,1,0)

```

*** PEACE ***
```{r}

df3$peace<-ifelse(df3$TR1==3,1,0)

```

*** BPL ***
```{r}
# df3["RC1A"]
df3$BPL<-ifelse(df3$RC1A==1|df3$RC1A==3,1,0)

```
*** PERMANENT JOB ***
```{r}
# df3["WS11A"]
# df3$perm_job<-ifelse(df3$RC1A==1,1,0)
hh_emp<- aggregate(WS11A~IDHH, data =df3, FUN = function(x) any(x ==  2))
```

```{r}
df3=left_join(df3, hh_emp, by = join_by(IDHH == IDHH))
df3$perm_job<-ifelse(df3$WS11A.y==TRUE,1,0)
```

*** WORK ***
```{r}
# df3["WS6YEAR"]
df3$work<-ifelse(df3$WS6YEAR>240,1,0)

```
*** LAND HOLDING ***
```{r}

# df3<- df3[df3$FM2 != -1, ]
# df3["FM4"]
# mean_col <- mean(df3$FM4)
# mean_col
df3$landHolding<-(df3$FM4+df3$FM6A)/df3$FM2
# summary(df3$landHolding)
```



*** AFTER ***
```{r}
df3$after<-0
df2$after<-1
```



*** MERGING PROCESS BEGINS ***

```{r}
df2005=df3%>% select(RO5,watch_TV,read_newspaper,num_adult,Widowed,female,work,landHolding,head,local_gov,hindu,muslim,obc,st,sc,perm_job,social_org,public_meet,literate,edu,urban,elec,collab,BPL,socialPen,peace,assetPoor,after,hh_ass)

df2011=df2%>% select(RO5,watch_TV,read_newspaper,num_adult,Widowed,female,work,landHolding,head,local_gov,hindu,muslim,obc,st,sc,perm_job,social_org,public_meet,literate,edu,urban,elec,collab,BPL,socialPen,peace,assetPoor,after,hh_ass)
```

```{r}
final_df_subset1 <- df2005[df2005$RO5>=45&df2005$landHolding>=0,]
# final_df_subset
final_df_subset2 <- df2011[df2011$RO5>=45&df2011$landHolding>=0, ]
# final_df_subset
final_df<-rbind(final_df_subset1,final_df_subset2)

```

```{r}
summary_df <- final_df_subset1 %>%
  summarise_all(list(
    mean = ~ mean(.),
    sd = ~ sd(.),
    min = ~ min(.),
    max = ~ max(.)
  ))

# Print summary dataframe
print(summary_df)
```


```{r}
summary_df <- final_df_subset2 %>%
  summarise_all(list(
    mean = ~ mean(.),
    sd = ~ sd(.),
    min = ~ min(.),
    max = ~ max(.)
  ))

# Print summary dataframe
print(summary_df)
```


```{r}
final_df
```
```{r}
mean_col <- mean(final_df$RO5)
mean_col
```
```{r}
# final_df$social_capital
final_df$BPL0<-ifelse(final_df$BPL==1 & final_df$after==0,1,0)
final_df$BPL1<-final_df$after*final_df$BPL
final_df$BPL2<-final_df$BPL*final_df$assetPoor
final_df$BPL3<-final_df$after*final_df$assetPoor*final_df$BPL


final_df$local0<-ifelse(final_df$local_gov==1 & final_df$after==0,1,0)
final_df$local1<-final_df$after*final_df$local_gov
final_df$local2<-final_df$assetPoor*final_df$local_gov
final_df$local3<-final_df$after*final_df$assetPoor*final_df$local_gov


final_df$pub0<-ifelse(final_df$public_meet==1 & final_df$after==0,1,0)
final_df$pub1<-final_df$after*final_df$public_meet
final_df$pub2<-final_df$assetPoor*final_df$public_meet
final_df$pub3<-final_df$after*final_df$assetPoor*final_df$public_meet


final_df$social0<-ifelse(final_df$social_org==1 & final_df$after==0,1,0)
final_df$social1<-final_df$after*final_df$social_org
final_df$social2<-final_df$assetPoor*final_df$social_org
final_df$social3<-final_df$after*final_df$assetPoor*final_df$social_org


final_df$land0<-ifelse(final_df$landHolding==1 & final_df$after==0,1,0)
final_df$land1<-final_df$after*final_df$landHolding
final_df$land2<-final_df$landHolding*final_df$assetPoor
final_df$land3<-final_df$after*final_df$assetPoor*final_df$landHolding


final_df$hass0<-ifelse(final_df$hh_ass==1 & final_df$after==0,1,0)
final_df$hass1<-final_df$after*final_df$hh_ass
final_df$hass2<-final_df$assetPoor*final_df$hh_ass
final_df$hass3<-final_df$after*final_df$assetPoor*final_df$hh_ass


final_df$age1<-final_df$after*final_df$RO5
final_df$age2<-final_df$assetPoor*final_df$RO5
final_df$age3<-final_df$after*final_df$assetPoor*final_df$RO5
```


```{r}
final_df$BPL00<-ifelse(final_df$BPL==1 & final_df$after==0 & final_df$assetPoor==0,1,0)
final_df$BPL01<-ifelse(final_df$BPL==1 & final_df$after==0 & final_df$assetPoor==1,1,0)
final_df$BPL10<-ifelse(final_df$BPL==1 & final_df$after==1 & final_df$assetPoor==0,1,0)
final_df$BPL11<-ifelse(final_df$BPL==1 & final_df$after==1 & final_df$assetPoor==1,1,0)


final_df$local00<-ifelse(final_df$local_gov==1 & final_df$after==0 & final_df$assetPoor==0,1,0)
final_df$local01<-ifelse(final_df$local_gov==1 & final_df$after==0 & final_df$assetPoor==1,1,0)
final_df$local10<-ifelse(final_df$local_gov==1 & final_df$after==1 & final_df$assetPoor==0,1,0)
final_df$local11<-ifelse(final_df$local_gov==1 & final_df$after==1 & final_df$assetPoor==1,1,0)


final_df$pub00<-ifelse(final_df$public_meet==1 & final_df$after==0 & final_df$assetPoor==0,1,0)
final_df$pub01<-ifelse(final_df$public_meet==1 & final_df$after==0 & final_df$assetPoor==1,1,0)
final_df$pub10<-ifelse(final_df$public_meet==1 & final_df$after==1 & final_df$assetPoor==0,1,0)
final_df$pub11<-ifelse(final_df$public_meet==1 & final_df$after==1 & final_df$assetPoor==1,1,0)


final_df$social00<-ifelse(final_df$social_org==1 & final_df$after==0 & final_df$assetPoor==0,1,0)
final_df$social01<-ifelse(final_df$social_org==1 & final_df$after==0 & final_df$assetPoor==1,1,0)
final_df$social10<-ifelse(final_df$social_org==1 & final_df$after==1 & final_df$assetPoor==0,1,0)
final_df$social11<-ifelse(final_df$social_org==1 & final_df$after==1 & final_df$assetPoor==1,1,0)


final_df$land00<-ifelse(final_df$landHolding==1 & final_df$after==0 & final_df$assetPoor==0,1,0)
final_df$land01<-ifelse(final_df$landHolding==1 & final_df$after==0 & final_df$assetPoor==1,1,0)
final_df$land10<-ifelse(final_df$landHolding==1 & final_df$after==1 & final_df$assetPoor==0,1,0)
final_df$land11<-ifelse(final_df$landHolding==1 & final_df$after==1 & final_df$assetPoor==1,1,0)
```


```{r}
library(ggcorrplot)
library(caret)
# create a correlation plot using ggplot2
cor_mat <- cor(final_df[, c("landHolding", "RO5", "hh_ass", "BPL", "local_gov", "public_meet", "social_org", "after")])
ggcorrplot(cor_mat, type = "lower", method = "circle", colors = c("#6D9EC1", "white", "#E46726"))

# check for high correlations (absolute values > 0.7)
high_cor <- findCorrelation(cor_mat, cutoff = 0.7, verbose = TRUE)

# print the names of the highly correlated variables
colnames(cor_mat)[high_cor]
```





*** FINAL REGRESSION MODEL ***
```{r}

# Split data into train and test sets
set.seed(456)
# Split the data into training and testing sets
trainIndex <- createDataPartition(final_df$socialPen, p = 0.7, list = FALSE)
trainIndex <- as.vector(trainIndex)
train <- final_df[trainIndex, ]
test <- final_df[-trainIndex, ]
train$socialPen <- as.numeric(as.character(train$socialPen))
test$socialPen <- as.numeric(as.character(test$socialPen))

```
```{r}
# summary(train_data$socialPen)
mean_col <- mean(train$socialPen)
mean_col
# summary(test_data$socialPen)
```

```{r}
mean_col <- mean(test$socialPen)
mean_col
```

```{r}

model <- lm(socialPen~BPL+local_gov+public_meet+social_org+RO5+unlist(landHolding)+hh_ass+after, data = train)
print(model)


```
```{r}

new_data <- data.frame(BPL=mean(final_df$BPL),local_gov=mean(final_df$local_gov),public_meet=mean(final_df$public_meet),social_org=mean(final_df$social_org),RO5=mean(final_df$RO5),landHolding=mean(final_df$landHolding),hh_ass=mean(final_df$hh_ass),after=mean(final_df$after))

prediction_mean <- predict(model, newdata = new_data)
#Creating confusion matrix
predictions <- predict(model, newdata = test)

```

```{r}
# # Create a confusion matrix
conf_mat <- table(Predicted = ifelse(predictions > prediction_mean, 1, 0),
                     Actual = test$socialPen)
# # 
# # Print the confusion matrix
conf_mat

```


```{r}
# create some example data
set.seed(123)

# calculate accuracy
accuracy <- sum(diag(conf_mat)) / sum(conf_mat)

# calculate precision
precision <- conf_mat[2, 2] / sum(conf_mat[, 2])

# calculate recall
recall <- conf_mat[2, 2] / sum(conf_mat[2, ])

# calculate specificity
specificity <- conf_mat[1, 1] / sum(conf_mat[1, ])

# calculate F1 score
f1_score <- 2 * precision * recall / (precision + recall)

# print results
cat("Confusion Matrix:\n")
print(conf_mat)

cat("\nAccuracy:", accuracy)
cat("\nPrecision:", precision)
cat("\nRecall:", recall)
cat("\nSpecificity:", specificity)
cat("\nF1 Score:", f1_score)

```

```{r}
conf_mat_df <- as.data.frame(conf_mat)

# Plot the confusion matrix
library(ggplot2)
ggplot(data = conf_mat_df, aes(x = Predicted, y = Actual, fill = Freq)) + 
  geom_tile() +
  scale_fill_gradient(low = "white", high = "steelblue", limits = c(0,max(conf_mat_df$Freq))) +
  labs(title = "Confusion Matrix", x = "Predicted", y = "Actual", fill = "Frequency") +
  theme(axis.text = element_text(size = 12), 
        axis.title = element_text(size = 14, face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))


```


```{r}

# Calculate mean squared error
mse <- mean((predictions -  prediction_mean)^2)
cat("MSE:", mse, "\n")

# Calculate R-squared
ss_res <- sum((predictions - test$socialPen)^2)
ss_tot <- sum((test$socialPen - mean(test$socialPen))^2)
r_squared <- 1 - (ss_res / ss_tot)
cat("R-squared:", r_squared, "\n")

```



```{r}

# Convert socialPen to factor
final_df$socialPen <- as.factor(final_df$socialPen)

# Filter the data to only include rows with socialPen == 1
plot_data <- final_df %>% filter(socialPen == 1)

# Plot the histogram with only red bars
ggplot(plot_data, aes(x = RO5, fill = socialPen)) +
  geom_histogram(binwidth = 1, position = "dodge") +
  scale_fill_manual(values = c("red")) +
  labs(x = "Age", y = "Count", fill = "Social Pension")

```
```{r}
model <- lm(socialPen~BPL0+BPL1+local0+local1+pub0+pub1+social0+social1, data = final_df)
print(model)
```
```{r}
model <- lm(socialPen~BPL, data = final_df_subset1)
print(model)
```
```{r}
model <- lm(socialPen~BPL+local_gov+public_meet+social_org, data =final_df_subset2)
print(model)

```
```{r}
model <- lm(socialPen~BPL00+BPL01+BPL10+BPL11+local00+local01+local10+local11+pub00+pub01+pub10+pub11+social00+social01+social10+social11, data = final_df)
print(model)
```
```{r}
model <- lm(socialPen~BPL+BPL1+BPL2+BPL3+local_gov+local1+local2+local3+public_meet+pub1+pub2+pub3+social_org+social1+social2+social3, data = final_df)
print(model)
```
```{r}
tester<-  subset(final_df, select = c(RO5,BPL,hh_ass,landHolding,local_gov,public_meet,social_org,watch_TV,peace,after))
# dff <- subset(dff, select = -c(v000, caseid,hw4,hw5,hw6,hw7,hw8,hw9,hw10,hw11,hw12,hw13,hw15,v008a,b18,s412a))
# Calculate feature importance using ROC curve area as score
roc_imp <- filterVarImp(x =tester[,1:ncol(tester)], y = final_df$socialPen, 
                         nonpara = TRUE, func = roc.area)

# Sort the score in decreasing order
roc_imp <- data.frame(cbind(variable = rownames(roc_imp), score = roc_imp[,1]))
roc_imp$score <- as.double(roc_imp$score)
roc_imp[order(roc_imp$score,decreasing = TRUE),]
```


```{r}

# Plot the top 10 features by ROC curve area
top_n <- 10
plot_data <- head(roc_imp, n = top_n)

ggplot(data = plot_data, aes(x = variable, y = score)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  ggtitle(paste0("Top ", top_n, " Feature Importance by ROC Curve Area")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Variable") +
  ylab("ROC Curve Area")

```

```{r}
set.seed(3033)
intra <- createDataPartition(y = final_df$socialPen, p= 0.9, list = FALSE)
intrain3 <- as.vector(intra)
# training3 <- final_df[intra,]
testy <- final_df[-intrain3,]
```



```{r}


set.seed(1111)

trainIndex <- createDataPartition(testy$socialPen, p = .7, 
                                  list = FALSE, 
                                  times = 1)
trainIndex <- as.vector(trainIndex)
training <-testy[trainIndex,]
testing <- testy[-trainIndex,]

cat("Training rows: ", nrow(training), "\n")


```
```{r}
# Randomly undersample the majority class
set.seed(123)
majority <- subset(training, socialPen == 0)
minority <- subset(training, socialPen == 1)
n_majority <- nrow(majority)
undersampled_majority <- majority[sample(n_majority, size = nrow(minority)), ]

# Combine the undersampled majority class and the minority class
balanced_training <- rbind(minority, undersampled_majority)

# Train the model on the balanced data
ctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 1)

lambda_grid <- expand.grid(alpha = 1, lambda = seq(0.12, 0.15, by = 0.005))

model <- train(socialPen ~ .,
               data = balanced_training,
               method = "glmnet",
               family = "binomial",
               preProc = c("center", "scale"),
               trControl = ctrl,
               tuneGrid = lambda_grid)


```
```{r}
print(model)
```
```{r}
predictions <- predict(model, testing)
sum(predictions != as_factor(testing$socialPen))
```

```{r}
confusionMatrix(predictions, as.factor(testing$socialPen))
```

```{r}
predictions_prob <- predict(model, testing, 'prob')
predictions_prob
```

```{r}

predictions_prob_1 <- predictions_prob[, 2]
predictions_2 <- ifelse(predictions_prob_1 > 0.5, 1, 0)

test_roc = roc(testing$socialPen ~ predictions_2, data = testing, plot = TRUE, print.auc = TRUE)
```


